plyranges: a grammar for transforming genomics data

### 2018-04-30 paper.Rmd
rework caption for overlaps figure.

```{r olaps-fig, echo = FALSE, out.width="400pt", fig.cap="Illustration of the three overlap join operators. Each join takes query and subject range as input (black and grey rectangles, respectively) with associated metadata (pink and orange rectangles respectively). An index for the join is computed via returning a Hits object, which contains the indices of where the subject overlaps the query range. This index is used to expand the query or (take the intersect) of the query ranges with subject ranges and return metadata associated with each input. This principle is gnerally applied through the `plyranges` DSL for both overlaps and nearest neighbour operations."}
knitr::include_graphics("diagrams/diagrams.002.png")
```

>>>>

```{r olaps-fig, echo = FALSE, out.width="400pt", fig.cap="Illustration of the three overlap join operators. Each join takes query and subject range as input (black and light gray rectangles, respectively). An index for the join is computed, returning a Hits object, which contains the indices of where the subject overlaps the query range. This index is used to expand the query ranges by where it was 'hit' by the subject ranges. The join semantics alter what is returned: for an *inner* join the query range is returned for each match, for an intersect *join* the intersection is taken between overlapping ranges, and for a *left* join all query ranges are returned even if the subject range does not overlap them. This principle is gnerally applied through the `plyranges` DSL for both overlaps and nearest neighbour operations."}
knitr::include_graphics("diagrams/diagrams.002.png")
```
